---
title: "Homework 5"
author: Aishwarya Anuraj
output: github_document
---

This is my solution to HW5

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(patchwork)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data. 

```{r, message = FALSE, warning = FALSE}
homicide_df = 
  read_csv("homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit

```{r, message = FALSE, warning = FALSE}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

prop test for a single city

```{r, message = FALSE, warning = FALSE}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
  ) %>% 
  broom::tidy()
```

Try to iterate..

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

### Part 1 

Reading just one file - 
```{r}
data_1 = read_csv("lda_data/con_01.csv")
```

Reading all the files and creating a dataframe 

```{r}
path_df = 
  tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(.x = path, ~read_csv(.x))
  ) %>% 
  unnest(data) %>% 
  mutate(
    path = str_replace(path, "lda_data/", ""),
    path = str_replace(path, ".csv", "")
    ) %>% 
  separate(path, into = c("study_arm", "subject_id"), sep = "_") %>% 
  mutate(
    subject_id = as.numeric(subject_id)
  )
  path_df =
    pivot_longer(
    path_df,
    week_1:week_8,
    names_to = "week", 
    values_to = "data")
```

### Part 2 
```{r spagett}
spagett_plot = 
  path_df %>% 
  group_by(study_arm, subject_id) %>% 
  ggplot(aes(x = week, y = data, group = subject_id, color = subject_id)) +
  geom_line() +
  geom_point(alpha = 0.5) +
  facet_grid(study_arm ~ .) +
  labs(
    title = "Observed Values for Control vs. Experimental Arms over Time",
    x = "Values",
    y = "Week of Observation"
  )
spagett_plot
```

Based on our spaghetti plot,the experimental group had an increase in values over time and the control group had a slight decrease in values over the course of observation. There was substantial variation within each group for any given week, from spreads of roughly 2.5 to 5 units.

